---
output: html_document
editor_options: 
  chunk_output_type: console
---
## Week 4
## Missing Data Quiz

```{r}
library(tidyverse)
library(VIM)
library(mice)
library(skimr)
```

```{r}
class_grades <- read_csv("class-grades.csv")
str(class_grades)
summary(class_grades)
# 1 - Tutorial, Midterm, TakeHome, Final
```

```{r}
vim_plot = aggr(class_grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
# 2 - Yes, TakeHome and Midterm
```


```{r}
# Row Wise Deletion
class_rowdel = class_grades %>% drop_na() 
# 3 - 89
skim(class_rowdel)
```

```{r}
class_coldel = class_grades %>% select(-Midterm, -Tutorial, -TakeHome, -Final)
vim_plot2 = aggr(class_coldel, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
skim(class_coldel)
# 4 - 2
```

#5 

The deletion of the rows with missing data from Task 3 has the more preferable outcome. Deleting the rows takes removes 10 individual observations, however, 89 of 99 observations are still available (roughly 90% of the starting data), as opposed to removing the columns, which removes 4 columns, leaving only prefix and assignment as the remaining variables. So, removing the rows leaves a significant amount of assorted data relative to the starting point, whereas removing columns, removes a significant portion of the total dataset, most of which did not contain a missing data piece. 

```{r}
set.seed(123)
imp_class = mice(class_grades, m=5, method='pmm', printFlag=FALSE)
summary(imp_class)
```

```{r}
class_complete = complete(imp_class) 
summary(class_complete)
# 68.33
```

